DeepSphere: a graph-based spherical CNN

### 2019-09-25 main.tex
Updates from Overleaf

\begin{abstract}
Selecting the right convolution for a spherical neural network is a delicate tradeoff between efficiency and  exactitude with respect of equivariance. DeepSphere, as a graph based method strikes as a controllable balance between these two desiderata. 
This contribution (i) studies empirically and theoretically how the construction of its underlying graph affects equivariance, and (ii) evaluates its performance on a large set of relevant problems.
Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.
% memory, computations, implementation complexity
\end{abstract}

@@

Several experiments were run with different architectures for DeepSphere (DS). Jiang architecture use a similar one as \cite{jiang2019sphericalcnn}, with only the convolutional operators replaced. DeepSphere only is the original architecture giving the best results, deeper and with four times more feature maps than Jiang architecture. And DeepSphere with a wider architecture is the same with two times the number of feature maps.

>>>>

\begin{abstract}
Selecting the right convolution for a spherical neural network is a delicate tradeoff between efficiency and  exactitude with respect to equivariance. DeepSphere, as a graph based method strikes as a controllable balance between these two desiderata. 
% Say something here about isotropy?
This contribution (i) studies empirically and theoretically how the construction of its underlying graph affects equivariance, and (ii) evaluates its performance on a large set of relevant problems.

Comparison with previous work on shape classification and climate event detection suggests that anisotropic filters are an unnecessary price to pay.
% memory, computations, implementation complexity
\end{abstract}

@@

Several experiments were run with different architectures for DeepSphere (DS). Jiang architecture use a similar one as \cite{jiang2019sphericalcnn}, with only the convolutional operators replaced. DeepSphere only is the original architecture giving the best results, deeper and with four times more feature maps than Jiang architecture. And the wider architecture is the same as the previous one with two times the number of feature maps.
